Liptschiz

### 2024-02-20 lipschitz/valabstraction.tex
update plots

\begin{tikzpicture}
	\begin{axis}[
		xlabel={$y_i$},
		ylabel={$\hat{y}_i$},
		xmin=-2, xmax=2,
		ymin=-2, ymax=2,
		axis lines=center,
		samples=100, 
	 unit vector ratio=1 1 1, scale=1.5, xtick   = {-2,2},
	 xticklabels = {$-\gamma_i$,$\gamma_i$},
	 yticklabels = {},
		]
		\addplot[blue, thick, fill=blue, fill opacity=0.4] {x} \closedcycle; 
		\addplot[blue, thick] {0};

			\node[label={above:$(-\gamma_i,-\gamma_i)$}] at (axis cs: -1.35, -2.1) {};

			\node[label={above:$(\gamma_i,\gamma_i)$}] at (axis cs: 1.45, 1.7) {};
	\end{axis}
\end{tikzpicture}

\vspace*{10ex}

The relation between $y_i$, $x_i$ and $\hat{y}_i$ is $$\hat{y}_i = \ReLU(x_i+y_i)-\ReLU(x_i).$$ And its plots is as follows:

>>>>

\begin{tikzpicture}
	\begin{axis}[
		xlabel={$y_i$},
		ylabel={$\hat{y}_i$},
		xmin=-2, xmax=2,
		ymin=-2, ymax=2,
		axis lines=center,
		samples=100, 
	 unit vector ratio=1 1 1, scale=1, xtick   = {-2,2},
	 xticklabels = {$-\gamma_i$,$\gamma_i$},
	 yticklabels = {},
		]
		\addplot[blue, thick, fill=blue, fill opacity=0.4] {x} \closedcycle; 
		\addplot[blue, thick] {0};

		\addplot[only marks, mark=*, mark size=2pt, blue] coordinates {(-2,-2)};
			\node[label={above:$(-\gamma_i,-\gamma_i)$}] at (axis cs: -1.35, -2.1) {};

				\addplot[only marks, mark=*, mark size=2pt, blue] coordinates {(2,2)};
			\node[label={above:$(\gamma_i,\gamma_i)$}] at (axis cs: 1.4, 1.5) {};
	\end{axis}
\end{tikzpicture}

The relation between $y_i$, $x_i$ and $\hat{y}_i$ is $\hat{y}_i = \ReLU(x_i+y_i)-\ReLU(x_i).$ And its plots is as follows:
